A holographic approach to the six-dimensional superconformal index

### 2022-10-14 fivebranes/main.tex
abstract

\begin{abstract}
We present a conjectural description of a semi-classical limit of the algebra of operators on a stack of finitely many fivebranes in $M$ theory at the level of the holomorphic twist.
Our approach is through the lens of twisted holography and utilizes a description of the minimal twist of eleven-dimensional supergravity. 
We find that local operators are modules for the exceptional linearly compact super Lie algebra $E(3|6)$. 
From the conjectural description of local operators we deduce closed formulas for the superconformal index of six-dimensional $\cN=(2,0)$ theories of type~$A_{N-1}$.
\end{abstract}

>>>>

\begin{abstract}
We present a conjectural description of the space of local operators on a stack of finitely many fivebranes in $M$ theory at the level of the holomorphic twist.
Our approach is through the lens of twisted holography and utilizes a description of the minimal twist of eleven-dimensional supergravity. 
We find that the spaces of local operators are modules for the exceptional linearly compact super Lie algebra $E(3|6)$.
From the conjectural description of local operators we deduce closed formulas for the superconformal index of six-dimensional $\cN=(2,0)$ theories of type~$A_{N-1}$.
\end{abstract}
